### 2023-03-17 paper/content.tex
Add changes in the paper manuscript

After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 103 windows selected previously. In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time. We obtained the magnetic moment and the direction for all 103 magnetic grains (Figure~\ref{real-data-stereograms}a). Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained. We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5. An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}. On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise. By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data. This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).

@@

\subsection{Prior information and uniqueness of solutions}
% simple synthetic
Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible. One way to circumvent the ambiguity is incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization. Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly. When the position of the source is known, it constrains the model to be as consistent as possible to the observed data, hence increasing the likelihood of obtaining unique solutions. \citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth. Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion. This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}. This remark is also observed with the our simple synthetic samples where the horizontal positions estimated slightly deviate from the true values, which implies very little misfits in the recovered magnetic directions. Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is cause by the ambiguity mentioned before. In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise, since that high-frequency noise sensibility is one of the main limitations of the technique.

%complex synthetic
The application in complex synthetic data allows observing the strengths and limitations of the proposed methodology. Some of the strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are high (e.g., $\geq 0.95$ and $\geq 10$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d). (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal. The main limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters. (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both. (iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion. As expected, there is a direct relationship between the dipole intensity and depth with the observed errors. It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps. Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.

\subsection{Reliability of dipole moment approximation}
% real samples
Our approach relies in the premise of assuming the magnetic anomaly within 
the data window is a response of a dipolar source. The latter is true when working 
with particle signals in the SD magnetic domain state, since they are uniform magnetized 
particles with strong dipolar anomaly. However, \cite{Nagy2017} reported
that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods
of time, being the stabler and also with strongly non-dipolar characteristics. 
Therefore application of the proposed algorithm to natural samples should fail for those PSD
particles. \cite{CortesOrtuno2022} give important insights about the matter, they 
showed that PSD state particles present more accurate inversion results when considering the non-dipole components for
small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
distances the dipole as approximations are remarkably accurate, as the
higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal. Thus, our approach can be
considered reasonable for working with both particle SD and PSD states signals. 
The latter happens mainly due to the sensor height being
usually greater than 5 $\mu m$, considering a particle on the immediate
surface of the sample the higher-order moments are already quite attenuated, thus 
circumventing the prominent problems described for non-dipolar components.

Despite the excellent signal/noise ratio that the SMM provided with the
proximity of the sensor to the sample, it is worth mentioning that the
measurement noise can still overshadow the responses of very weak/small, or
deep particles, generating unreliable inversion results. Therefore, it is
necessary to keep a check to determine if the inversion reached a satisfactory
result, such as the coefficient of determination and the
signal-to-noise ratio suggested by \citep{CortesOrtuno2021}.

@@

To recover magnetic direction and moment we only need to assume that the
sources have their central positions known (so we apply Euler deconvolution)
and that their magnetization are uniform. This last premise aligns with the
theory of magnetically stable particles SD (and the PSD ones at a reasonable
sensor height), which is the basis of classical paleomagnetism. Also, there is
no need for any kind of prior knowledge other than the observed magnetic
anomaly, and the structural index of the sources. Therefore, this method can be
quickly replicated in a dataset of thin sections of rocks to obtain the
distributions of magnetic directions of each source identified in the sample.

The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise. While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable sizes and depths. The real sample data positively answered the question of the algorithm's ability to deal with rocks thin sections. But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test. We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).

@@

The image re-scaling and blob detection though the Laplacian of Gaussian method
were performed with the scikit-image library \citep{VanderWalt2014}. We also used Matplotlib \citep{Hunter2007} for plotting the figures, numpy \citep{Harris2020} and scipy \citep{2020SciPy-NMeth} for all performed calculations. Verde \citep{verde2018} was used to generate data grids and to perform the regional residual separation, while the upward continuation filter was calculated using Harmonica \citep{harmonica2020}. The Choclo library \citep{choclo2022} provided kernel functions utilized in the forward and inverse problems. Loops were parallelized with the aid of Numba just-in-time compilation \citep{lam2015numba}. Lastly, the xarray library \citep{hoyer2017xarray} offered a fast and powerful tool to work with multi-dimensional datasets allowing an easy way to alteration, visualization and extraction of data with advanced indexing techniques.

The QDM image data is available at CITE A DATAVERSE/FIGSHARE ARCHIVE under the
CC-XX license.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
This research project was supported by the Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) - grant 162704/2021-6 and by the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) - grant 2021/08379-5, the opinions, hypotheses and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP. We also acknowledge the support of the Royal Society \textcolor{red}{[insert grant number]} for this research project. We are indebted to the developers and maintainers of the open-source software without which this work would not have been possible.

>>>>

After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 103 windows selected previously. In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time. We obtained the magnetic moment and the direction for all 103 magnetic grains (Figure~\ref{real-data-stereograms}a). Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained. We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5. An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}. On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise. By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data. This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b). Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite outnumbers the hematite.

@@

\subsection{Prior Information and Uniqueness of Solutions}
Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible. One way to circumvent the ambiguity is incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization. Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly. When the position of the source is known, it constrains the model to be as consistent as possible to the observed data, hence increasing the likelihood of obtaining unique solutions. \citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth. Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion. This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}. This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies very little misfits in the recovered magnetic directions. Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is probably caused by the ambiguities. In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise, since that high-frequency noise sensibility is one of the ED's main limitations.

\subsection{A Critical Examination of Windows Approach}%: Identifying its Strengths and Limitations}

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure. In the first type of approach the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions and non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial  \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}. This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}. However, this assumption is not always true when dealing with complex samples with a magnetic mineral fabric with more than one stable directions, which leads to the same drawbacks as the classic paleomagnetic measurements using bulk sample. The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as microcomputed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021} . The latter further allows uniquely estimation of dipolar magnetic configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}. Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with microCT weaknesses. The MicroCT is a popular non-destructive technique for high resolution imaging of materials internal structures, and yet, it is accompanied of some limitations when it comes to the paleomagnetic studies: firstly, the technique has spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained the single-domain magnetite (Cnudde et al., 2006; Cnudde & Boone, 2013, de Groot 2018). The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation (Cnudde & Boone, 2013). But, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.

Our proposed methodology has the goal of finding each individual source’s dipole moment components without the trouble of mechanically select cropped data or the needing any type of additional information. However, to better examine its advantages and disadvantages we first need to point out the strengths and weaknesses of the technique used in the detection of sources,  The Laplacian of Gaussian (LoG) kernel (Marr and Hildreth (XXXX)). The LoG is a computer imaging technique that is able to identify regions where the intensity changes abruptly by convolving the image with a LoG filter, resulted of a combination of the Gaussian blur and Laplacian filter (CITE BOOK). The Laplacian filter is able to highlight the regions where the intensity changes in a rapidly way. On the other hand, the Gaussian blur is a smoothing filter for high-frequency noise, which reduces the likelihood to generate artifacts. Hence, the result of this LoG operation can identify blobs as regions above a certain threshold, this threshold crossing determines what are brighter spots (local maxima) surrounded by a darker background. It is also scale-invariant by detecting blobs of different sizes and intensities, a feature achieved by varying the sizes of the Gaussian filter. The advantages of the methodology are: (i) high-accuracy blob detection; (ii) scale-invariant for images with different intensities/sizes objects; while also being (iii) robust to the presence of noise due to the Gaussian smoothing filter. While the main drawbacks of the LoG blob algorithms are: (i) being computationally expensive/time consuming when dealing with larger images and (ii) the requirement of parameters adjustment, such as the threshold and the kernel sizes.

The total gradient anomaly (TGA) might be considered the ideal image to be used as input for the LoG blob detection algorithm for potential field studies (micro and/or macroscale). The TGA highlights the subsurface sources by generating a map of positive magnetic anomalies concentrated within their edges. This technique is widely used in aeromagnetic surveys to determine sources’ boundaries by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution. Hence. The application for micromagnetic measurements comes with all the advantages and drawbacks previous mentioned, nonetheless the windows generated isolate the main magnetic signal’s region of each source. This guarantees that our thresholding approach (see section~\ref{dipole-reliability}), for both ED and dipolar inversion, is performed using the critical slice of the micromagnetic data, giving satisfactory parameters approximation and fast results as shown in the synthetic data.

The complex synthetic data allows a better observation of the strengths and limitations of the windows approach. The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d). (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal. The major limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters. (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both. (iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values). As expected, there is a direct relationship between the dipole intensity and depth with the observed errors. It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps. Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.

\subsection{Reliability of Dipole Moment Approximation}\label{dipole-reliability}

Our approach relies in the premise of assuming the magnetic anomaly within 
the data window is a response of a dipolar source. The latter is true when working 
with particle signals in the SD magnetic domain state, since they are uniform magnetized 
particles with strong dipolar anomaly. However, \cite{Nagy2017} reported
that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods
of time, being the stabler and also with strongly non-dipolar characteristics. 
Therefore application of the proposed algorithm to natural samples should fail for those PSD
particles. \cite{CortesOrtuno2022} give important insights about the matter, they 
showed that PSD state particles present more accurate inversion results when considering the non-dipole components for
small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
distances the dipole as approximations are remarkably accurate, as the
higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal. Thus, our approach can be
considered reasonable for working with both particle SD and PSD states signals. 
The latter happens mainly due to the sensor height being
usually greater than 5 $\mu m$, considering a particle on the immediate
surface of the sample the higher-order moments are already quite attenuated, thus 
circumventing the prominent problems described for non-dipolar components.

Despite the excellent signal/noise ratio that the SMM provided with the
proximity of the sensor to the sample, it is worth mentioning that the
measurement noise can still overshadow the responses of very weak/small, or
deep particles, generating unreliable inversion results. Therefore, it is
necessary to keep a check to determine if the inversion reached a satisfactory
prediction, such as the coefficient of determination and the
signal-to-noise ratio suggested by \citep{CortesOrtuno2021}.

@@

To recover magnetic direction and moment we only need to assume that the
sources have their central positions known (so we apply Euler deconvolution)
and that their magnetization are uniform. This last premise aligns with the
theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable
sensor-sample height, which is the basis of classical paleomagnetism. Also, there is
no need for any kind of prior knowledge other than the observed magnetic
anomaly, and the structural index of the sources. Therefore, this method can be
quickly replicated in a dataset of thin sections of rocks to obtain the
distributions of magnetic directions of each source identified in the sample.

The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise. While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths. The real sample data positively answered the question of the algorithm's ability to deal with rocks thin sections. But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test. We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).

@@

The image re-scaling and blob detection though the Laplacian of Gaussian method
were performed with the Scikit-image library \citep{VanderWalt2014}. We also used Matplotlib \citep{Hunter2007} for plotting the figures and Mplstereonet \citep{xxxxx} for stereograms. Basic calculations were performed using Numpy \citep{Harris2020} and Scipy \citep{2020SciPy-NMeth}. Verde \citep{verde2018} was used to generate data grids and to perform the regional residual separation, while the upward continuation filter was calculated using Harmonica \citep{harmonica2020}. The Choclo library \citep{choclo2022} provided kernel functions utilized in the forward and inverse problems. Loops were parallelized with the aid of Numba just-in-time compilation \citep{lam2015numba}. Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful tool for working with multi-dimensional datasets allowing an easy way of data visualization and extraction with advanced indexing techniques.

The QDM image data is available at \textcolor{red}{CITE A DATAVERSE/FIGSHARE ARCHIVE under the CC-XX license}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
This research project was supported by the Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) - grant 162704/2021-6 and by the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) - grant 2021/08379-5, the opinions, hypotheses and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP. We also acknowledge the support of the Royal Society ex \textcolor{red}{[insert grant number]} for this research project. We are indebted to the developers and maintainers of the open-source software without which this work would not have been possible.
